<<<<<<< HEAD
---
title: "Finance Dashboard"
output: html_document
---

Read in packages and get the data ready
```{r}
library(tidyverse)
library(flexdashboard)
library(readxl)
library(janitor)
library(ggthemes)
library(scales)
library(directlabels)
library(highcharter)

money <- read_xlsx('Retirement.xlsx') %>% 
  clean_names()

money_long <- money %>% 
  pivot_longer(!c(investments, rate, fee, location, description, shares), names_to = "date", values_to = "value") %>% 
  mutate(date = str_remove(date, 'x')) %>% 
  mutate(date = as.Date(as.numeric(date), origin = "1899-12-30")) %>% 
  mutate(description_simple = str_split(description, "-")) %>% 
  separate(description, into = "description_simple", remove = F, sep = "-") %>% 
  mutate(description_simple = trimws(description_simple)) %>% 
  mutate(value_description = ifelse(value < 10000, "<10k",
                                    ifelse(value <50000, "10k-50k",
                                           ifelse(value < 100000, "50k-100k",
                                                  ">100k"))))

year_sum <- money_long %>% 
  filter(date == max(date)) %>% 
  summarize(sum(value, na.rm = T)) %>% 
  as.numeric()

last_month <- money_long %>% 
  filter(date == max(date)) %>% 
  mutate(value_perc = value*100/year_sum)

```


Pie chart of investment type by value
```{r}
last_month %>% 
  group_by(description_simple) %>% 
  summarise(total_perc = sum(value_perc, na.rm = T)) %>% 
  hchart(
    type = 'pie', 
    hcaes(x= description_simple, y = total_perc)
  )
```


Pie chart of stocks by value
```{r}
last_month %>% 
  filter(description_simple == "Stock") %>% 
  group_by(description) %>% 
  summarise(total_perc = sum(value_perc, na.rm = T)) %>% 
  hchart(
    type = 'pie', 
    hcaes(x= description, y = total_perc)
  )
```

Pie chart of investment by location
```{r}
last_month %>% 
  group_by(location) %>% 
  summarise(total_perc = sum(value_perc, na.rm = T)) %>% 
  hchart(
    type = 'pie', 
    hcaes(x= location, y = total_perc)
  )
```

Investment value by type over time - bar
```{r}
money_long %>% 
  group_by(date, description_simple) %>% 
  summarise(sum_value = sum(value, na.rm = T)) %>% 
  hchart(
    type = 'column', 
    hcaes(x = date, y = sum_value, group = description_simple), stacking = 'normal'
  )
```

Investment value by type over time - line
```{r}
money_long %>% 
  group_by(date, description_simple) %>% 
  summarise(sum_value = sum(value, na.rm = T)) %>% 
  hchart(
    type = 'line', 
    hcaes(x = date, y = sum_value, group = description_simple)
  )
```


Investment value per investment over time
```{r}
money_long %>% 
  group_by(date, investments, description_simple) %>% 
  summarise(sum_value = sum(value, na.rm = T)) %>% 
    hchart(
    type = 'line', 
    hcaes(x = date, y = sum_value, group = investments)
  )

=======
---
title: "Finance Dashboard"
output: html_document
---

Read in packages and get the data ready
```{r}
library(tidyverse)
library(flexdashboard)
library(readxl)
library(janitor)
library(ggthemes)
library(scales)
library(directlabels)
library(highcharter)

money <- read_xlsx('Retirement.xlsx') %>% 
  clean_names()

money_long <- money %>% 
  pivot_longer(!c(investments, rate, fee, location, description, shares), names_to = "date", values_to = "value") %>% 
  mutate(date = str_remove(date, 'x')) %>% 
  mutate(date = as.Date(as.numeric(date), origin = "1899-12-30")) %>% 
  mutate(description_simple = str_split(description, "-")) %>% 
  separate(description, into = "description_simple", remove = F, sep = "-") %>% 
  mutate(description_simple = trimws(description_simple)) %>% 
  mutate(value_description = ifelse(value < 10000, "<10k",
                                    ifelse(value <50000, "10k-50k",
                                           ifelse(value < 100000, "50k-100k",
                                                  ">100k"))))

year_sum <- money_long %>% 
  filter(date == max(date)) %>% 
  summarize(sum(value, na.rm = T)) %>% 
  as.numeric()

last_month <- money_long %>% 
  filter(date == max(date)) %>% 
  mutate(value_perc = value*100/year_sum)

```


Pie chart of investment type by value
```{r}
last_month %>% 
  group_by(description_simple) %>% 
  summarise(total_perc = sum(value_perc, na.rm = T)) %>% 
  hchart(
    type = 'pie', 
    hcaes(x= description_simple, y = total_perc)
  )
```


Pie chart of stocks by value
```{r}
last_month %>% 
  filter(description_simple == "Stock") %>% 
  group_by(description) %>% 
  summarise(total_perc = sum(value_perc, na.rm = T)) %>% 
  hchart(
    type = 'pie', 
    hcaes(x= description, y = total_perc)
  )
```

Pie chart of investment by location
```{r}
last_month %>% 
  group_by(location) %>% 
  summarise(total_perc = sum(value_perc, na.rm = T)) %>% 
  hchart(
    type = 'pie', 
    hcaes(x= location, y = total_perc)
  )
```

Investment value by type over time - bar
```{r}
money_long %>% 
  group_by(date, description_simple) %>% 
  summarise(sum_value = sum(value, na.rm = T)) %>% 
  hchart(
    type = 'column', 
    hcaes(x = date, y = sum_value, group = description_simple), stacking = 'normal'
  )
```

Investment value by type over time - line
```{r}
money_long %>% 
  group_by(date, description_simple) %>% 
  summarise(sum_value = sum(value, na.rm = T)) %>% 
  hchart(
    type = 'line', 
    hcaes(x = date, y = sum_value, group = description_simple)
  )
```


Investment value per investment over time
```{r}
money_long %>% 
  group_by(date, investments, description_simple) %>% 
  summarise(sum_value = sum(value, na.rm = T)) %>% 
    hchart(
    type = 'line', 
    hcaes(x = date, y = sum_value, group = investments)
  )

>>>>>>> f6d30883f3aace6b2af634e79bd70de1e3455241
```